Deriving a precise Newtonian equation for the time it takes two separated bodies in an isolated system to collide due to the gravitational force

### 2022-10-30 paper/draft.tex
draft fixes
fixes

\section{Introduction}
During my calculus lessons I wondered how we could derive an equation to calculate the time it takes for two separated objects to collide by virtue of their mutual gravitational attraction. In other words, how can we combine both the gravitational force equation
\begin{align}
    F_g = G \frac{m_1 m_2}{r^2}
\end{align}
and Newton's Second Law of Motion
\begin{align}
    F = ma
\end{align}
to derive an equation that solves for the time it takes them to collide if you specify the masses of both objects and their initial separation.
\\
\\
After stumbling across some specific tricks, I finally managed to solve this and since I am still unable to find any solid resource about it online, I decided to share the solution here for anyone who may find this interesting or finds himself in a similar situation.
\\
\\
Notes:
\begin{itemize}
    \item We do not take into account any relativistic effects and in this solution we also assume that the objects have no initial velocity at their starting positions.
    \item I may sometimes go into a bit of detail regarding the methods used to solve this problem, which might be tedious if you already know them, but I wanted this solution to be as self-contained as it could be, and I actually learned a lot of them working through this exercise.
\end{itemize}

@@

@@

Substituting this back into (todo) gives us our solution to the cosine squared integral

>>>>

\section{Introduction}
During my calculus lessons I wondered how we could derive an equation to calculate the time it takes for two separated objects to collide by virtue of their mutual gravitational attraction. In other words, how can we combine both the gravitational force equation
\begin{align*}
    F_g = G \frac{m_1 m_2}{r^2}
\end{align*}
and Newton's Second Law of Motion
\begin{align*}
    F = ma
\end{align*}
to derive an equation that solves for the time it takes them to collide if you specify the masses of both objects and their initial separation.
\\
\\
After stumbling across some specific tricks, I finally managed to solve this and since I am still unable to find any solid resource about it online, I decided to share the solution here for anyone who may find this interesting or finds himself in a similar situation.
\\
\\
Notes:
\begin{itemize}
    \item We do not take into account any relativistic effects and in this solution we also assume that the objects have no initial velocity at their starting positions.
    \item I may sometimes go into a bit of detail regarding the methods used to solve this problem, which might be tedious if you already know them, but I wanted this solution to be as self-contained as it could be, and I actually learned a lot of them working through this exercise.
\end{itemize}

@@

    \label{eq:temp_right}

@@

Substituting this back into (\ref{eq:temp_right}) gives us our solution to the cosine squared integral
